---
format:
  pdf:
    keep-tex: true
    titlepage: true
    include-in-header: 
       text: |
         \usepackage{fvextra}
         \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
bibliography: references.bib
csl: ieee.csl
link-citations: true
include-before-body:
  text: |
    \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
      showspaces = false,
      showtabs = false,
      breaksymbolleft={},
      breaklines
      % Note: setting commandchars=\\\{\} here will cause an error 
    }
header-includes: |
  \AtBeginDocument{
    \title{
      Exploratory Data Analysis (Holiday Movies)
    }
    \author{
      Md Nazmul Hossain (0843082) \\ 
      A A Talha Talukder (XXXXXXX) \\ 
      Nibedita Mallik (XXXXXXX)
    }
    <!-- \date{ -->
    <!--   \today -->
    <!-- } -->
    \maketitle
    \begin{center}
      \large{\textbf{Group number: 09}}  \\
      \large{\textbf{Project ID: 07}} 
    \end{center}
  }
  \usepackage{listings}
  \lstset{
    breaklines=true,
    breakatwhitespace=true,
    basicstyle=\ttfamily\footnotesize,
    frame=single
  }
  \usepackage{ragged2e}
  \justifying
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{graphicx}
  \usepackage{float}
  \floatplacement{table}{H}
  \floatplacement{figure}{H}
  \usepackage{caption}
  \captionsetup[table]{skip=10pt}
editor: visual
output: 
  pdf: 
    documentclass: article
    titlepage: true
  html: 
    toc: true
  word: default
appendix: true
execute:
  comment: false
---

\newpage

```{r}
#| echo: false
#| label: load libraries
#| message: false
#| warning: false

# Some global settings, data preparation and variables to ease the usage of different variables 
# without worrying to create or load in multiple places

# load tidyverse
library(tidyverse)
# load kableExtra
library(kableExtra)

# read data from github
holiday_movies <- readr::read_csv('holiday_movies.csv')
holiday_movie_genres <- readr::read_csv('holiday_movie_genres.csv')

# create a data frame where every genre name is a column
# and each will have value 0 or 1. Value 1 means it beolngs to that genre, 0 means doesnt belongs to that
holiday_movies_ext <- holiday_movies %>%
  mutate(copy_genres = genres) %>%  # keep the original genres column intact
  separate_rows(copy_genres, sep = ",") %>%  # split genres into separate rows
  mutate(dummy = 1) %>%  # create a dummy variable for each genre
  pivot_wider(names_from = copy_genres, values_from = dummy, values_fill = 0)  # pivot to wide format, fill with 0

# view the resulting data frame
# head(holiday_movies_ext)

# set theme
theme_set(theme_bw()) 
```

# Introduction

Movie data introduction and the citation style we are going to use is IEEE [@HeQiang2022ASPB]. The tidytuesday reference is here [@tidytuesday].

# Data Collection

We have collected the data from tidytuesday [@tidytuesday].

The data we have collected is showing as below in @tbl-top-ten-genres-by-movie-count.

```{r}
#| echo: false
#| warning: false
#| label: tbl-top-ten-genres-by-movie-count
#| tbl-cap: "Top 10 renres by number of movies."

# get top 10 genres by movie count
top_10_gnr_mv_count <- holiday_movies %>%
  separate_rows(genres, sep = ",") %>%
  group_by(genres) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  head(10)

# display the table
kable(top_10_gnr_mv_count, format = "latex", booktabs = TRUE)
```

# Data Summaries

We are going to split this section into two sub-sections, as with numerical and graphical summaries.

## Nemerical Summaries

The total number of observations from the survey received is: `r nrow(holiday_movies)`. The table shows in @tbl-top-ten-genres-by-movie-count.

## Graphical Summaries

We will take help of several graphical plots here to describe the data. Listed as below.

### Box Plot

Box plot details will go here ...

### Bar Plot

Bar plot details will go here and sample with caption as below  @fig-top-ten-genres-by-movie-count.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-top-ten-genres-by-movie-count
#| fig-cap: "Top 10 genres by number of movies."
#| fig-height: 6
#| fig-width: 8
#| fig-align: center

# display the bar plot
ggplot(top_10_gnr_mv_count, aes(x = reorder(genres, -Count), y = Count, fill = genres)) +
  geom_bar(stat = "identity") +
  labs(x = "Genres", y = "Count")
```


### Linear Regression (e.g. with Scatter Plot)

Linear regression details.

# Discussion

The discussion details.

# Correlations (if applicable)

Correlation details.

# Conclusion

Here goes the conclusion section!

\newpage

# References

::: {#refs}
::: 

# Acknowledgements

- We would like to give thanks to the tidytuesday for the relevant data.
- Additionally, we would took help to debug tables, plot and data transformation codes in Stack overflow code snippets and Copilot.

\newpage

# Appendix

## Code

```{r}
#| echo: true 
#| eval: false 
#| ref-label: !expr knitr::all_labels()
```

